Simulation Study: Informative Covariate (cubic)

### 2018-04-19 datasets/simulations/simulations-informative-cubic.Rmd
Remove nmids arg for FDR reg from sims

@@

```{r}
bdplus <- bd
bdplus <- addBMethod(bdplus, "scott-theoretical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'theoretical',
                     control = list(lambda = 0.01, nmids = nmids))
bdplus <- addBMethod(bdplus, "scott-empirical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'empirical',
                     control = list(lambda = 0.01, nmids = nmids))
```

>>>>

For comparison, we also include the ASH q-values.

```{r}
bd <- addBMethod(bd, "ashq", ashr::ash, ashr::get_qvalue,
                 betahat = effect_size, sebetahat = SE)
```

@@

```{r}
bdplus <- bd
bdplus <- addBMethod(bdplus, "scott-theoretical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'theoretical',
                     control = list(lambda = 0.01))
bdplus <- addBMethod(bdplus, "scott-empirical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'empirical',
                     control = list(lambda = 0.01))
```
